\documentclass[main]{subfiles}
\begin{document}
\setcounter{section}{1}
\section{Basic notions}

%@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
% summarizes: graphs, isomorphism, adjacency matrix, paths, cycles, connectivity
% author: Vanessa Leite
% This was never tested in the exam before

\subsection{Graphs}
\textbf{Graph} $G = (V,E)$. $V$ = finite set of objects called vertices. $E$ = collection of pairs of vertices called edges.

Examples:
\begin{itemize}
\item $V$ = set of people in a room. $E$ = pairs of people who new each other before enter the room.
\item $V$ = set of cities in some country. $E$ = pairs of cities connected by direct road.
\item $V$ = pages of people on facebook. $E$ = people who are friends
\end{itemize}

\textit{Definition}: $e(G)$ = number of edges in $G$. $e(G) = |E(G)|$

Some remarks:
\begin{itemize}
\item we will consider mostly \textbf{simple graphs}
\item if there are more than one edge between some vertices, the graph is called \textbf{multigraph}
\item \textbf{loop} is an edge connecting a vertice to itself.
\end{itemize}

\textit{Definition}: if $(u,v)$ is an edge, we say $u$ is \textbf{adjacent} to $v$. We also say that $e$ is incident to vertices $u$ and $v$.
\begin{itemize}
\item we call two edges $e$ and $e'$ \textbf{incident} if $e \cap e' \neq 0$
\item if $e=(u,v)$ then $v$ is a \textbf{neighbor} of $u$
\end{itemize}

$N(u)$ is the set of all neighbors of $u$, i. e., set of all $v$ where $(u,v)$ is an edge.
$|N(u)|$ is the degree of $u$

\textit{Puzzle}: Show that every graph has at least two vertices of the same degree


\subsection{Isomorphism}

\subsection{Adjacency matrix}

\subsection{Paths}

\subsection{Cycles}

\subsection{Connectivity}

\todo[inline]{add content}

\end{document}