\documentclass[main]{subfiles}
\begin{document}

%@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
% summarizes Vertex and edge connectivity, blocks, 2-connectivity, Mader's theorem, Menger's theorem
% author: Vanessa Leite

\section{Connectivity}

\subsection{Vertex connectivity}

\textbf{Vertex cut} in a connected graph $G = (V,E)$ is a set $S \subseteq V$ such that $G \setminus S = G[V \setminus S]$ has at least two connected components. A \textbf{cut vertex} is a vertex $v$ whose deletion disconnects the graph.\\
$G$ is called \textbf{k-connected} if $|V(G)| > k$ and if $G \setminus X$ is connected for every set $X \subseteq V$ with $|X| < k$. A graph $G$ is k-connected if and only if $|V(G)| > k$ and deleting any set $|X| < k$ leave $G$ connected.

Example:
\todo[inline]{Add the example here}

Let's $K(G)$\footnote{$K$ is the greek letter Kappa} be the maximum $k$ subject to $G$ is k-connected.

Example:
$G = K_{n}: K(G) = n-1$
$G = K_{m,n}, m < n: K(G) = m$

\textit{Proof}: Let $|S| \leq m-1$. So, $G \setminus S$ has at least one vertex on each part and these vertices connects everything.
\\
\textit{Claim}: $K(G) \leq \delta(G)$
\textit{Proof}: Let $v$ be a vertex of $G$ subject to $d(v) = \delta(G)$, delete all neighbors of $v$ ($N(v)$):
\begin{itemize}
\item if $|G| \geq \delta(G) + 1$ and exists a set of size $\delta(G)$ which disconnects the graph, then $K(G) \leq \delta(G)$
\item if $|G| \geq \delta(G) + 2$, then indeed, deleting $N(v)$ disconnects $G$ therefore $K(G) \leq \delta(G)$
\item if $|G| = \delta(G) + 1$, by definition $K(G) \leq \delta(G)$
\end{itemize}

Note: high minimum degree does not imply connectivity, for instance, consider two disjoint copies of $K_{n}$
\todo[inline]{Add the example here}

\subsubsection{Mader Theorem}
Every grapg with average degree of, at least, $4k$ has a k-connected subgraph.
\textit{Proof} by induction: for $k = 0$ we just have one vertex, for $k=1$ we just have one edge, so, let's consider $k\geq 2$.
\textit{Claim}: let $G$ be an n-vertex graph with m edges.
\begin{enumerate}
\item $n \geq 2k - 1$
\item $m \geq (2k-3)(n-k+1)+1$
\end{enumerate}
If both statements holds, then $G$ contains a k-connected subgraph

Note average degree of $4k$ implies:
\begin{enumerate}
\item existence of one vertex $v$ with $d(v) \geq 4k$, then $n \geq 4k + 1$
\item $m \geq \frac{4kn}{2} = 2kn$
\end{enumerate}

Let's check that $n = 2k-1$ statement is true. Then $m \geq (2k-3)(n-k+1)+1 = (n-2)\frac{n+1}{2}+1 = \frac{n(n-1)}{2}$.\footnote{given $n=2k-1$ then $k=\frac{n+1}{2}$} So, $G$ is a complete graph. $G$ itself is $n-1 = 2k-2 \geq $ k-connected

\subsubsection{edge connectivity}

\subsubsection{blocks}

\subsubsection{2-connectivity}

\subsubsection{Mader's theorem}

\subsection{Menger's theorem}

\end{document}